---
title: "HAR hotspots"
author: "Viktoriia Kuznetcova"
date: "9/27/2017"
output:
  html_document:
    toc: TRUE
    toc_depth: 4
    self_contained: yes
    theme: null
---
```{r echo=FALSE}
library(jsonlite)
har <- fromJSON(filename, simplifyDataFrame = TRUE, flatten = TRUE)
entries <- har$log$entries

# Aggregating timing results per request to understand how are the resources cached
timings <- aggregate(time ~ request.url, data=entries, FUN=length)
names(timings) <- c("request", "count")
timings$total <- aggregate(time ~ request.url, data=entries, FUN=sum)$time
timings$average <- aggregate(time ~ request.url, data=entries, FUN=mean)$time
timings$median <- aggregate(time ~ request.url, data=entries, FUN=median)$time
timings$max <- aggregate(time ~ request.url, data=entries, FUN=max)$time
timings$min <- aggregate(time ~ request.url, data=entries, FUN=min)$time
repeatingRequests <- subset(timings, timings$count > 1)
problemsDetected <- subset(repeatingRequests, min > 0)
problemsDetected <- problemsDetected[order(-problemsDetected$count),]

# Selecting resources that are cached later than they should be, i.e. they are loaded from the server multiple times
cachedStats <- aggregate(pageref ~ request.url+time, data=entries, FUN=length)
cachedStatsFromServer <- aggregate(time ~ request.url, data = cachedStats[cachedStats$time > 0,], FUN=length)
cachedStatsFail <- subset(cachedStatsFromServer, time > 1)
cachedStatsFail <- cachedStatsFail[order(-cachedStatsFail$time),]
names(cachedStatsFail) <- c("Request", "Samples not cached")

# Finding whether there are static resources that are not gzipped
notCompressed <- subset(entries, entries$response.content.compression == 0 & entries$response.content.mimeType %in% c("text/javascript", "text/css", "image/png", "image/gif"))
notCompressed <- notCompressed[, c("pageref", "request.url", "response.bodySize", "response._transferSize", "response.content.size")]
notCompressed <- notCompressed[order(-notCompressed$response.content.size),]
```

##Hotspots
Potential problems with caching were identified in the provided har file `r {filename}`.

###Not cached
These are the requests that were called more than once, yet were not cached at all.

They need to be cached unless they are dynamically generated.
```{r results="asis", echo=FALSE}
library(xtable)
print(xtable(problemsDetected), type="html", include.rownames=FALSE,latex.environments = "left")
```

###Cached too late
These are the requests that were called more than once, were eventually cached, but not right away. It usually happens when a few iframes on the page request the same resource.

It might make sense to lazy preload such resources earlier in the user workflow, so they are already in browser cache by the time we hit the page with windowlets.
```{r results="asis", echo=FALSE}
library(xtable)
print(xtable(cachedStatsFail), type="html", include.rownames=FALSE,latex.environments = "left")
```

###Uncompressed static resources
All static resources should be compressed to save time on loading them from the server.
```{r results="asis", echo=FALSE}
print(xtable(notCompressed), type="html", include.rownames=FALSE,latex.environments = "left")
```

##Details
All the requests for detailed analysis
```{r results="asis", echo=FALSE}
library(xtable)
print(xtable(timings), type="html", include.rownames=FALSE,latex.environments = "left")
```